% Please refer to http://www.bilkent.edu.tr/~provost/jourlist/journal.htm 
% 
% Format: First Author, Second Author, Third Author, etc., “Title of article,” Title of Journal, Volume, No, Pages, Year.
% Example: I.W. Jones, L. Corwin, “Correlation in Power Residue Generated Random Numbers,” Journal of Computational 
% 	Physics, vol. 12, no. 6, 373-382, 2014.

\begin{enumerate}[i)]
\item {\bf Published} % (attach copies of each of the manuscripts – see v.1 in box A.1 above)

\begin{enumerate}

  \item        
    The 1000 Genomes Project Consortium. ``A global reference for human genetic variation'', {\em Nature}, Oct 1; 526 (7571):98-74, 2015.\\
    {\it Elif Dal, Fatma Kahveci, and Can Alkan contributed to the structural variation analyses.}

  \item        
  P.H. Sudmant, T. Rausch, E.J. Gardner,  R.E. Handsaker, A. Abyzov, J. Huddleston, Y. Zhang, K. Ye, G. Jun, M.H-Y. Fritz, M.K. Konkel, A. Malhotra, A.M. Stütz, X. Shi, F.P. Casale, J. Chen, 
  F. Hormozdiari, G. Dayama, K. Chen, M. Malig, M.J.P. Chaisson, K. Walter, S. Meiers, S. Kashin, E. Garrison, A. Auton, H.Y.K. Lam, X. J. Mu, \calkan, D. Antaki, T. Bae, E. Cerveira, P. Chines, Z. Chong, 
  L. Clarke, E. Dal, L. Ding, S. Emery, X. Fan, M. Gujral, F. Kahveci, J.M. Kidd, Y. Kong, E-W. Lameijer, S. McCarthy, P. Flicek, R.A.Gibbs, G. Marth, C.E. Mason, A. Menelaou, D.M. Muzny, 
  B.J. Nelson, A. Noor, N.F. Parrish, M. Pendleton, A. Quitadamo, B. Raeder, E.E. Schadt, M. Romanovitch, A. Schlattl, R. Sebra, A.A. Shabalin, A. Untergasser, 
  J.A. Walker, M. Wang, F. Yu, C. Zhang, J. Zhang, X. Zheng-Bradley, W. Zhou, T. Zichner, J. Sebat, M.A. Batzer, S.A. McCarroll, 
  The 1000 Genomes Project Consortium, R.E. Mills, M.B. Gerstein, A. Bashir, O. Stegle, S.E. Devine, C. Lee, E.E. Eichler, J.O. Korbel. 
  `` An integrated map of structural variation in 2,504 human genomes'',
  {\em Nature}, Oct 1; 526 (7571):75–81, 2015.

  \item        
   P. Kavak, B. Yüksel, S. Aksu, M.O. Kulekci, T. Güngör, F. Hach, S.C. Sahinalp, Turkish Human Genome Project, {\bf {\underline {C. Alkan}}}$^\ddag$,
  M.S. Sağıroğlu$^\ddag$.    
  ``Robustness of massively parallel sequencing platforms'',
 {\em PLoS ONE},  Sep 18;10(9):e0138259, 2015.  

  \item        
  D. Lee, F. Hormozdiari, H. Xin, F. Hach, O. Mutlu$^\ddag$,  {\bf {\underline {C. Alkan}}}$^\ddag$.
  ``Fast and accurate mapping of Complete Genomics reads'',
  {\em Methods}, Jun;79-80:3-10, 2015. 

  \item        
 H. Xin, J. Greth, J. Emmons, G. Pekhimenko, C. Kingsford, {\bf {\underline{C. Alkan}}}$^\ddag$,  O. Mutlu$^\ddag$. 
 ``Shifted Hamming Distance: a fast and accurate SIMD-friendly filter to accelerate alignment verification in read mapping'',
{\em Bioinformatics},  May 15;31(10):1553-60, 2015.

  \item        
   C. Kucuk, B. Jiang, X. Hu, W. Zhang, J. Chan, W. Xiao, N. Lack,   {\bf {\underline {C. Alkan}}},  J. Williams, K. Avery, P. Kavak, A. Scuto, E. Sen,  P. Gaulard, L. Staudt, J. Iqbal,  W. Zhang,  A. Cornish, Q. Gong, Q.  Yang, H. Sun, F. d'Amore, S. Leppä, W. Liu, K. Fu, L. de Leval, T. McKeithan.
   ``Activating mutations of STAT5B and STAT3 in lymphomas derived from $\gamma\delta$-T or NK cells'',
 {\em Nature Communications}, Jan 14;6:6025, 2015.


\end{enumerate}

\junk{
\item {\bf Accepted} % (attach copies of each of the manuscripts and the acceptance letters - see v.1 and v.2 in box A.1 above)
}

\end{enumerate}

