% List the seminars, workshops and lectures given at other universities, companies, or organizations. Please indicate if you have received any monetary support from the organizing institution.

% Format: “Seminar/Lecture Title,” date, place, monetary support, if any.
\begin{enumerate}
\item
  Invited Speaker,
  {\bf A cryptocurrency with DNA Sequence Alignment as Proof-of-work.}
  9$^{th}$ International Symposium on Health Informatics and Bioinformatics (HIBIT 2015),
   Muğla, Turkey, October 16, 2015. Received reimbursement for travel and lodging.
\item
  Workshop Talk, 
  {\bf Can you really anonymize the donors of genomic data in today's digital world?}
  10$^{th}$ International Workshop on Data Privacy Management (DPM 2015), 
  September 21, 2015, Vienna, Austria.
\item
  Workshop Short Talk, 
  {\bf Characterization of structural variation and segmental duplications for the GiaB Project.}
  Genome in a Bottle Workshop, National Institute of Standards and Technology, Gaithersburg, MD, USA,
  August 27, 2015.
\item
  Invited Speaker, 
  {\bf Discovery of large genomic inversions using pooled clone sequencing.}
  Georgia Institute of Technology, Atlanta, GA, USA, August 26, 2015. Received reimbursement for travel and lodging.
\item
  Conference Talk, 
  {\bf Coinami: A cryptocurrency with DNA Sequence Alignment as Proof-of-work.}
  High Throughput Sequencing Algorithms and Applications (HiTSeq 2015), Dublin, Ireland, July 10, 2015.
\item
  Invited Speaker, 
  {\bf Discovery of large genomic inversions using pooled clone sequencing.}
  İzmir Biomedicine and Genome Center, Dokuz Eylül University, İzmir, Turkey, April 20, 2015. Received reimbursement for travel and lodging.
\item
  Invited Speaker, 
  {\bf High Throughput Sequencing and Bioinformatics for characterization of diseases of genomic origin.}
  24$^{th}$ Conference of the Asian Pacific Associaton for the Study of the Liver (APASL 2015), İstanbul, Turkey, March 11, 2015. Received reimbursement for travel and lodging.

\end{enumerate}
