% List the graduate students whom you supervised during the period and their research topics.

% Format: Name of student, degree, “Title of thesis,” period of supervision, (expected) graduation date.
% Example: Mark Kohlman, M.S., “Design and Implementation of Multi-purpose MCIS Machines,” September 2005 - June 2014, expected graduation 2014.


\paragraph{Advisees:}


\begin{enumerate}
\item Elif Dal, M.S. student, since Fall 2012, expected graduation in Spring 2015.
\item Fatma Balcı, Ph.D. student, since Fall 2014.
\item Pınar Kavak, Ph.D. student at the Boğaziçi University, ``Development of hybrid assembly algorithms for cross-platform datasets.'', co-advising with Tunga Güngör since Spring 2012.
\item Shatlyk Ashyralyyev,  Ph.D. student, co-advising with Cevdet Aykanat, since Fall 2013.
\item Volkan Yazar,  Ph.D. student, Bilkent University Department of Molecular Biology and Genetics, co-advised with Ebru Erbay, since September 2013.
\item Marzieh Eslami-Rasekh, M.S. student, since Spring 2014, switched from Uğur Doğrusöz. Expected graduation in Spring 2015.
\item Azita Nouri M.S. student, co-advising with Özcan Öztürk, since Spring 2014.
\item Handan Kulan,  Ph.D. student, since Fall 2014.
\item Gülfem Demir M.S. student, since Fall 2014.
\item Mohammed Alser,  Ph.D. student, since Fall 2014.
\end{enumerate}

\paragraph{Alumnus:}

\begin{enumerate}
\item Fatma Balcı, M.Sc. ``Bias correction in finding copy number variation using read depth based methods in exome sequencing data''. Graduated in Summer 2014.
\end{enumerate}

\paragraph{Thesis committees (current):}

\begin{enumerate}
\item Arif Yılmaz: Ph.D. candidate, Bioinformatics, since December 2012. Advisor: Yeşim Aydın Son. Middle East Technical University, Ankara, Turkey.

\item Özlem Tufanlı: Ph.D. candidate, Molecular Biology and Genetics, since Fall 2013. Advisor: Ebru Erbay. Bilkent University, Ankara, Turkey.

\item Evrim Tekeli: Ph.D. candidate, Anthropology, since Fall 2013. Advisor: Timur Gültekin. Ankara University, Ankara, Turkey.

\item Fahrettin Can Koyuncu: Ph.D. candidate, Computer Engineering, since Spring 2014. Advisor: Çiğdem Gündüz Demir. Bilkent University, Ankara, Turkey.

\item Yogesh Paudel: Ph.D. candidate, Biostatistics and Informatics, since Fall 2014. Advisor: Martien A.M. Groenen. Institut für Biostatistik und Informatik in Medizin und Alternsforschung, Wageningen University, Wageningen, The Netherlands.
\end{enumerate}

\paragraph{Thesis committees (alumni):}
\begin{enumerate}
\item Mehmet Başaran: M.Sc. Computer Engineering, completed in Fall 2014. Advisor: Cevdet Aykanat. Bilkent University, Ankara, Turkey.

\item Gülşah Merve Dal: Ph.D. candidate, Molecular Biology and Genetics, completed in Fall 2014. Advisor: Tayfun Özçelik. Bilkent University, Ankara, Turkey
\end{enumerate}
