% List the students whom you supervised in 2014 and their project topics.

% Format: Name of the student(s), project type (Industrial/Senior/Term/other), "Topic/Name of project", status (i.e. completed or in progress), date of completion (expected date if in progress).

\paragraph{CS490 Introduction to Research course}
\begin{enumerate}
\item 
Can Fırtına: ``Fast filters for pairwise comparison of short and long NGS reads'', Spring 2015. 
\item 
Damla Şenol: ``Transmission Patterns Discovery of Genome Structural Variations among Generations of a Family'', Spring 2015. 
\end{enumerate}

\paragraph{Extra curriculum projects:}

\begin{enumerate}
\item 
     Abdullah Alperen, extra curriculum implementation project, ``Read mapping to de Bruijn graphs'', since Spring 2015. 
\item 
      Halil İbrahim Özercan, extra curriculum implementation project, ``A cryptocurrency that uses DNA sequence alignment as proof-of-work'', since Spring 2015. 
\item 
      Mert İnan, extra curriculum implementation project, ``A cryptocurrency that uses DNA sequence alignment as proof-of-work'', since Spring 2015. 
\item 
      Ege Berkay Gülcan, extra curriculum implementation project, ``A cryptocurrency that uses DNA sequence alignment as proof-of-work'', since Spring 2015. 
\item 
      Ertuğrul Akay, extra curriculum implementation project, ``A cryptocurrency that uses DNA sequence alignment as proof-of-work'', since Spring 2015. 
\item
      Burcu Çanakçı, extra curriculum implementation project, ``Novel sequence detection algorithm'', since Spring 2015. 
\item
      Atıl Vural, extra curriculum implementation project, ``Web interface for DNA variation analysis'', since Spring 2015. 
\item
      Ayhun Tekat, extra curriculum implementation project, ``Integrated structural variation discovery algorithm'', Summer 2015. 
\end{enumerate}

\paragraph{Senior Project - Supervisor:}

\begin{enumerate} 
\item Özgür Öney, Ahmet Safa Kayhan, Selçuk Gülcan, Ateş Balcı, Fırat Özbay, ``Espionage Game'', in progress, September 2015 - May 2016.
\item F. Tuğba Doğan, Cihad Öğe, Fatma Koç, Cem Sevim, Gizem Göktepe, Senior Project, ``Biopeer'', September 2014 - May 2015
\item Ahmet Kerim Şenol, Alper Gündoğdu, Yusuf Özkaya, Halil İbrahim Özercan, Senior Project, ``Coinami'', September 2014 - May 2015
\item Ozan Can Altıok, Metin Can Siper, Umut Utku Çalış, Halil Türkoğlu, Sami Şimşekli, Senior Project, ``Anotice'', September 2014 - May 2015
\item Gökhan Çetin, Gökhan Güler, Utku Bozoklu, Ekrem Doğan, Senior Project, ``Touravel'', September 2014 - May 2015
\item Yeliz Kurt, Dilan Yatan, Damla Özgen, Ahmet Ertan, Basri Karademir, Senior Project, ``SUN: Social University Network'', September 2014 - May 2015
\end{enumerate}

\paragraph{Senior Project - Jury Member:}

\begin{enumerate}
\item Mert Uygur, Erdi Atalay, Metin Enes Uçan, Atıl Vural, ``Intelligent Attendance'', September 2015 - May 2016.
\item Süleyman Aslan, Kaan Mert Berkem, Fatih Karaoğlanoğlu, Abdullah Çağlar Öksüz, ``APEX'', September 2015 - May 2016.
\item Berkay Çakır, Burak Özmen, İsmail Can Dereli, Umut Barış İşler, ``Health App'', September 2015 - May 2016.
\item Cihat Halit, F. Enes Kocayusufoğlu, Ömer Sinan Şahin, Sanem Elbaşı, ``Padio'', September 2015 - May 2016.
\item Can Fırtına, Ayhun Tekat, Ali Yeşilyaprak, Mustafa Kamil İman, Senior Project, ``Emotion Engine'', September 2014 – May 2015.
\item Simge Yücel, Can Özel, Ezgi Coşkun, Damla Şenol, Gencer Sünbül, Senior Project, ``iGarson'', September 2014 – May 2015.
\item Aliye Begüm Akbay, Osman Hakan Can, Müge Tetik, Senior Project, ``Clewear'', September 2014 – May 2015.
\item Ahmet Cihat Ünaldı, Fatma Zehra Uludağ, Işıl İrem Tekeş, Yusuf Öncül, Zeynep Uyanık, Senior Project, ``Shopakolik'', September 2014 – May 2015.
\end{enumerate}
