\begin{enumerate}

\item Evaluate your performance and achievements in the past year vis á vis your own goals. 

At the end of last year I received a grant from the European Molecular Biology Organization, and the project started in April 2013. In addition I received an award from the Science Academy of Turkey under the BAGEP program. 

I hired two new PhD students: Shatlyk Ashyralyev, co-advised with Cevdet Aykanat, and Volkan Yazar, who is registered to the MBG department, co-advised with Tayfun Özçelik and Ebru Erbay. Shatlyk will work in my TUBITAK 1001 project, and he will develop algorithms for hybrid genome assembly using hypergraphs, and also distributed graph processing frameworks. Volkan's project will be more applied, and he will search for gene mutations that play a role in obesity and diabetes.

For my NIH project, I acquired newly developed Tesla GPGPUs and Intel Xeon Phi manycore devices. A student in Cevdet Aykanat's group (Oğuz Selvitopi) developed parallel algorithms that make use of multi-core and manycore processors. The GPGPU implementation is partially ready, and Shatlyk Ashyralyev is working on finishing the first version of the algorithm.

In 2013, I published 4 papers with Bilkent affiliations, and submitted two more. 


\item Describe your goals pertaining to your work and your contributions to your department and the university in the next two years. 

I plan to use my grants to further my research in the area of bioinformatics and computational genomics. Here are my aims, listed for each grant:

\begin{enumerate}

\item NIH: I plan to continue working with Prof. Aykanat, and his PhD student Oğuz Selvitopi to continue our effforts to parallelize some of the bioinformatics tools. In a new collaboration with Assoc Prof Özcan Öztürk, we will hire a new M.Sc. student starting in Spring 2014 to continue the previous GPGPU work and develop algorithms for the new Tesla K20 GPGPUs that have a better memory layout and provide dynamic parallelism.
\item Marie Curie: I plan to hire a Ph.D. student, or postdoctoral fellow to work on my Marie Curie project, which involves development of elegant combinatorial algorithms to optimize genomic variation detection. I believe this project may be too complicated for a M.Sc. project, therefore I will try to hire either a postdoctoral fellow or a Ph.D. student.
\item TÜBİTAK: I will continue advising my two M.Sc. students (Elif Dal and Fatma Balcı), and a Ph.D. student at the Boğaziçi University (Pınar Kavak) for developing genome assembly and sequence correction algorithms and applying them to real datasets. In addition, Shatlyk Ashyralyev will work on algorithms based on hypergraphs and distributed graph processing frameworks for the same project.
\item EMBO: This project is the application of bioinformatic methods to genomic data to discover gene 	  mutations that lead to obesity and diabetes. I will collaborate with Tayfun Özçelik and Ebru Erbay on   	  this project, and Volkan Yazar will be responsible of analyzing genomic data.

\end{enumerate}

\end{enumerate}

