% Describe any changes to this form which you feel would improve its evaluative sensitivity and effectiveness.

I believe the citation reports section of this form can be substantially improved. As it stands, we are asked to print the full information of any paper that cited our previous work including their bibliography, and then mark our papers within their bibliographies. This is menial work: in fact more efforts need to be spent by researchers with high number of citations. Instead, each faculty can be asked to be simply registered to a service provided by the ISI Web of Knowledge - hosted at \url{http://www.researcherid.com} - that can be used to generate basic citation report analyses such as the number of citations per year, among others. Then only this basic report can be submitted in hard copy, which will be 1-2 pages, and save everyone’s time in preparing and evaluating the annual survey. The IDs given by this service can be also reported to the Provost Office, and they can be tracked for verification if there are inconsistent reports. Alternatively, the ORCID database can be used for the same purpose: \url{https://orcid.org}

Another problem is the Teaching section. The information in Subsection B1 is available in STARS: although the guidelines ask to report those that are not available on STARS, the questions themselves specifically request information that are available on STARS. Same for Subsection B6. And Subsection B4 -- as we are all required to teach the same number of courses, and each course has a fixed number of class hours, this question is also needless.
